---
title: "Project"
author: "Yizhe Wang"
date: "10/24/2017"
output: html_document
---

The Time period we decided on is from :2012-01-01 to 2016-12-31, on monthly basis.

Loading Libraries
```{r}
library(quantmod)
library(PerformanceAnalytics)
library(ggplot2)
library(tseries)
library(dplyr)
```


Loading ff variables(rf, SMB, HML, etc.)
```{r}
ff = read.csv("F-F_Research_Data_Factors.CSV", header = TRUE)
ff = ff[which(ff$X >= 201201 & ff$X <= 201612),]
rownames(ff) = 1:nrow(ff)
```

Loading Tickers of S&P 500
```{r}
sym = as.character( read.csv('http://trading.chrisconlan.com/SPstocks_current.csv', stringsAsFactors = FALSE, header = FALSE)[,1] )
sym = sym[-which(sym == "BHI")]
sym = sym[-which(sym == "BRK.B")]
sym = sym[-which(sym == "BF.B")]
sym = sym[-which(sym == "CAT")]
sym = sym[-which(sym == "CLX")]
#sym = sym[-which(sym == "")]
sym = sym[-which(sym == "HAR")]
sym = sym[-which(sym == "LLTC")]
sym = sym[-which(sym == "MJN")]
sym = sym[-which(sym == "RAI")]
sym = sym[-which(sym == "TSO")]
sym = sym[-which(sym == "WFM")]
sym = sym[-which(sym == "YHOO")]


```


Loading Stock Adjusted Closing Price
```{r, warning=FALSE}
total = as.data.frame(get.hist.quote(instrument = sym[1], start="2011-12-01", end="2016-12-31",quote = "Adjusted",  provider = "yahoo",compression = "monthly"))
colnames(total) = sym[1]
total = data.frame(date = as.character(rownames(total)),value = total)

for (i in 2:length(sym)) {
temp = as.data.frame(get.hist.quote(instrument = sym[i], start="2011-12-01", end="2016-12-31",quote = "Adjusted",  provider = "yahoo",compression = "monthly"))
colnames(temp) = sym[i]
temp = data.frame(date = as.character(rownames(temp)),value = temp)
total = full_join(total, temp, by = "date")
}

```


Delete columns with NA value (Does not fit the requirement of 60 month chosen)
```{r}
new_total = total[ , colSums(is.na(total)) == 0]
rownames(new_total) = new_total$date
new_total = new_total[, -1]
```

Return
```{r}
return_total = data.frame(matrix(ncol = length(new_total[1,]), nrow = 60))
for(j in 1:length(new_total[1,])) {
  for(i in 1:60) {
    return_total[i,j] = (new_total[i+1,j] - new_total[i,j])/(new_total[i,j])
  }
}
colnames(return_total) = colnames(new_total)
rownames(return_total) = rownames(new_total[-1,])
```

All available S&P 500 stocks adjusted return -> View(return_total)

Finding Alphas and Betas
```{r}
alpha = data.frame(matrix(ncol = length(return_total[1,]), nrow = 1))
colnames(alpha) = colnames(return_total)
rownames(alpha) = "alpha"

beta = data.frame(matrix(ncol = length(return_total[1,]), nrow = 1))
colnames(beta) = colnames(return_total)
rownames(beta) = "beta"

for (i in 1:length(return_total[1,])) {
  fit = lm(return_total[,i] ~ ff$Mkt.RF)
  result = summary(fit)
  alpha[1,i] = result$coefficients[1,1]
  beta[1,i] = result$coefficients[2,1]
}
```

Randomly Pick

a = return_total[,sample(ncol(return_total), 10)]
b = order(abs(beta), decreasing = T)
b = b[c(45,90,135,180,225,270,315,350,395,440)]

From random
 [1] "DVN"  "IBM"  "APA"  "MSI"  "TDG"  "CMI"  "CELG" "BA"   "VRSK" "PM"  
From selecting based on beta
 [1] "BLK"  "FFIV" "MAR"  "PXD"  "AAL"  "MDLZ" "CINF" "MRK"  "KO"   "FRT"

```{r}
port_random_index = c("DVN", "IBM", "APA",  "MSI",  "TDG",  "CMI",  "CELG", "BA",   "VRSK", "PM")
port_beta_index = c("BLK",  "FFIV", "MAR",  "PXD",  "AAL",  "MDLZ", "CINF", "MRK",  "KO",   "FRT")
```


```{r}
port_random = c()
for (i in 1:10) {
  port_random = c(port_random,which(colnames(return_total) == port_random_index[i]))
}

port_beta = c()
for (i in 1:10) {
  port_beta = c(port_beta,which(colnames(return_total) == port_beta_index[i]))
}
```

Expected return
```{r}
expected_mkt.f = mean(ff$Mkt.RF)/100
expected_r = mean(ff$RF)/100


expected_random = data.frame(matrix(ncol = 1, nrow = 10))
rownames(expected_random) = c("DVN", "IBM", "APA",  "MSI",  "TDG",  "CMI",  "CELG", "BA",   "VRSK", "PM")
colnames(expected_random) = "Expected Return"
for (i in 1:10) {
  expected_random[i,1] = expected_r + expected_mkt.f * as.numeric(beta[port_random[i]]) 
}
random_matrix = return_total[port_random]

expected_beta = data.frame(matrix(ncol = 1, nrow = 10))
rownames(expected_beta) = c("DVN", "IBM", "APA",  "MSI",  "TDG",  "CMI",  "CELG", "BA",   "VRSK", "PM")
colnames(expected_beta) = "Expected Return"
for (i in 1:10) {
  expected_beta[i,1] = expected_r + expected_mkt.f * as.numeric(beta[port_beta[i]]) 
}
beta_matrix = return_total[port_beta]
```


```{r}
cov_matrix_random = data.frame(matrix(ncol = 10, nrow = 10)) 
cov_matrix_random = cov(random_matrix)

cov_matrix_beta = data.frame(matrix(ncol = 10, nrow = 10)) 
cov_matrix_beta = cov(beta_matrix)

matrix1 = data.frame(matrix(ncol = 1, nrow = 10))
for (i in 1:10) {
  matrix1[i,1] = 1
}

A = (solve(as.vector(cov_matrix_random)) %*% matrix1) %*% t(expected_random)

```

